Scaffolder - Software for Microbial Genome Scaffolding.

### 2011-02-01 text/src/article.tex
Revise last section of results

\subsection*{Discussion of scaffolder approach} %{{{2

The main aims of scaffolder are two fold. The first is usability and the second is reproducibility.

@@

Scaffolder is designed to be as simple to use as possible. Assuming the
existence of Ruby and RubyGems, scaffolder can be installed with a single
command. Scaffolder uses a minimal and compact syntax to described the
scaffold. This syntax is simple to construct and edit whilst being succinct and
readable in describing how the scaffold was constructed. Scaffolder provides
extensive documentation both for the command line tools and for the Scaffolder
Ruby API.

@@

Constructing a genome sequence using a plain text scaffold file means the same
sequence is always output for the same file. The sequence produced from
manually joining separate contigs in a text editor can not be reliably
reproduced. Constructing the scaffold in a plain text file means that the
sequence is reproducible. Furthermore the source of each region in final
sequence can be identified. The scaffold file provides a readable record of
how the sequence was constructed. The scaffold file also means the scaffold is
easier to edit once already constructed. Much more difficult to do when working
on the sequence alone. The YAML text format is also much easier to compare
differences using standard diff commands. This makes scaffold files much more
simple to store in version control and to see the stages in the construction
of the genome sequence.

>>>>

\subsection*{Discussion of Scaffolder Approach} %{{{2

The main aims of scaffolder are two foldfold. The first is produce easy to
install and simplifies the task of genome finishing. The second aim is to
allow to create a tool to facilitate reproducibility in the task of joining
large nucleotide sequences together. \pb

@@

Scaffolder is designed to be simple to use as possible. Assuming the existence
of Ruby and RubyGems, scaffolder can be installed in a single command line
step. Scaffolder uses a minimal and compact syntax to described the genome
scaffold. This syntax is simple to construct and edit whilst being succinct
and readable. This aims to allow creating a genome scaffold to relatively
simple to do in a common text editor. Furthermore scaffolder provides
extensive documentation both for the command line tools and for the Scaffolder
Ruby API. Therefore should any part of the scaffolder tool be unclear the
documentation should make an solution easy to find. \pb

@@

Constructing a genome sequence using a plain text scaffold file means the same
sequence is always output for the same file. Joining large nucleotide
sequences manually cannot however be reliably reproduced. The layout of the
scaffold file furthermore provides a human readable record of how the sequence
was constructed. \pb

Configuring the final sequence in the scaffold file means the build is easier
to edit once already constructed compared with working on the sequence alone.
The YAML text format is also much easier to compare differences using standard
text comparison tools such as diff. This makes scaffold files easier to store
in version control systems. This affords genome scaffolding the same benefits
enjoyed by software developers. \pb
